Multi-modality Imagery Database for Plant Phenotyping

### 2015-05-04 datapaper_baseline.tex
xm's first edits

\subsection{Multi-leaf segmentation and tracking framework}
We apply our automatic multi-leaf segmentation and tracking framework~\cite{yin2014a,yin2014b} to the testing set of Arabidopsis fluorescence imagery to provide a baseline.
We treat all images in $9$ days as a video from first image on the first day to the last image in the last day.
As shown in Figure~\ref{fig:methodOverview}, the input of this framework is a plant video and a set of predefined templates with various shapes, scales, and orientations.
To generate the template set, we first select $12$ templates with different aspect ratios from the labeled images in the training set together with the corresponding tip locations.
For each template, we scale it to $10$ different sizes in order to cover the entire range of leaf sizes in the database.
For each scale template, we rotate every $15^{\circ}$ to generate $24$ templates at different orientations.
Tip locations will be scaled and rotated accordingly.
Finally, we generate $2,880$ leaf templates.

@@

\subsection{Performance and analysis}
We apply our algorithm on all $144$ frames of each video and evaluate the performance on labeled $36$ frames.
Leaf alignment is applied to the last frame of each video.
Figure~\ref{fig:alignResult} shows some examples of leaf alignment results.
Our framework works very well on segmenting large leaves with no overlap to neighbor leaves.
For overlapping leaves, it becomes more challenging as the edges between the overlapping area are more difficult to be detected.
However, when the overlapping leaves are further away from the center, they will have a higher chance to be detected as shown in $(c)$ of Figure~\ref{fig:alignResult}.
When the overlapping leaves are close to the center, smaller leaves will be covered by larger leaves as shown in $(a), (d), (e)$ of Figure~\ref{fig:alignResult}.

Leaf alignment provides the leaf candidates for tracking over time.
Figure~\ref{fig:trackExample} shows one leaf tracking result. 
The leaf template transformation works well for most of the leaves.
As plant grows, younger leaves may grow faster than older leaves and occlude the older leaves.
As shown in Fig.~\ref{fig:trackExample} (b), purple leaf replaces the red leaf at day $6$.
Our backward tracking algorithm tracks leaves from the last frame to the first frame.
The two leaves are still being considered as one leaf (ID $8$) in day $4$ and day $3$. 
Leaf $8$ in day $1$ and $2$ is considered as leaf ID switch and will be not count as consistently tracked leaf. 
However, it is still been considered as well aligned and segmented leaves. 
%Leaves will be deleted when it becomes small and the leaf underneath it will be detected.

@@

\includegraphics[trim= 90 60 100 5, clip, width=.14\textwidth]{Figures/AlignPerformance/9_2}&
\includegraphics[trim= 90 60 100 5, clip, width=.14\textwidth]{Figures/AlignPerformance/10_2}&
\includegraphics[trim= 90 60 100 5, clip, width=.14\textwidth]{Figures/AlignPerformance/11_2}&
\includegraphics[trim= 90 60 100 5, clip, width=.14\textwidth]{Figures/AlignPerformance/12_2}&
\includegraphics[trim= 90 60 100 5, clip, width=.14\textwidth]{Figures/AlignPerformance/14_2}&
\includegraphics[trim= 90 60 100 5, clip, width=.14\textwidth]{Figures/AlignPerformance/15_2}\\
(a) & (b) & (c) & (d) & (e) & (f) \\
\end{tabular}
\caption{Leaf alignment results on the last frame of $6$ plant videos. First row shows the original image. Second row shows the alignment result with red points denote the boundary of the leaf templates in the blue bounding boxes. The numbers on the leaves are the leaf IDs representing the order of the leaf being selected and they will be consistent during tracking.}
\label{fig:alignResult}
\end{centering}
\end{figure*}

@@

& Day 1 & Day 2 & Day 3 & Day 4 & Day 5 & Day 6 & Day 7 & Day 8 & Day 9 \\
\end{tabular}
\caption{Tracking result for one video with one frame for each day. $(1)$ Example frames in the video. $(2)$. Leaf label result overlaid with tip locations. $(3)$ Leaf tracking result. We show one frame for each day. }
\label{fig:trackExample}
\end{centering}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[width=.98\textwidth]{Figures/performance.pdf}\\
\caption{Performance of the baseline method.}
\label{fig:performance}
\end{figure*}

For quantitative evaluation, we vary $\tau$ from $0$ to $1$ and generate the first three evaluation metrics, as shown in Fig.~\ref{fig:performance}.
{\it{ULR}} decreases as $\tau$ increases as more leaves are being considered as matched leaves.
As $\tau$ keep increasing, {\it{ULR}} approaches a constant value, which is the different number in leaf counting that results from both miss detection and false alarms.
{\it{LE}} increases as $\tau$ increases as it includes leaves with larger tip-based errors for averaging.
{\it{TC}} increases as $\tau$ increases as more leaves are being considered as correctly tracked leaves.
Note that {\it{TC}} is influenced by the length of frames evaluated for each video. 
As the longer frames we evaluate, the higher chance tracking will be failed. 
Overall, our method can detect $87\%$ and track $50\%$ of all labeled leaves with less than $20\%$ average tip-based errors.

>>>>

\subsection{Multi-leaf Segmentation and Tracking Framework}
We apply our automatic multi-leaf segmentation and tracking framework~\cite{yin2014a,yin2014b} to the testing set of Arabidopsis fluorescence imagery to provide a baseline.
We treat all images in $9$ days as a video from first image on the first day to the last image in the last day.
As shown in Figure~\ref{fig:methodOverview}, the input of this framework is a plant video and a set of predefined templates with various shapes, scales, and orientations.
To generate the template set, we first select $12$ templates with different aspect ratios from the labeled images in the training set together with the corresponding tip locations.
For each template, we scale it to $10$ different sizes in order to cover the entire range of leaf sizes in the database.
For each scale template, we rotate every $15^{\circ}$ to generate $24$ templates at different orientations.
Tip locations will be scaled and rotated accordingly.
Finally, we generate $2,880$ leaf templates.

@@

@@

\includegraphics[trim= 90 60 100 5, clip, width=.14\textwidth]{Figures/AlignPerformance/9_2}&
\includegraphics[trim= 90 60 100 5, clip, width=.14\textwidth]{Figures/AlignPerformance/10_2}&
\includegraphics[trim= 90 60 100 5, clip, width=.14\textwidth]{Figures/AlignPerformance/11_2}&
\includegraphics[trim= 90 60 100 5, clip, width=.14\textwidth]{Figures/AlignPerformance/12_2}&
\includegraphics[trim= 90 60 100 5, clip, width=.14\textwidth]{Figures/AlignPerformance/14_2}&
\includegraphics[trim= 90 60 100 5, clip, width=.14\textwidth]{Figures/AlignPerformance/15_2}\\
(a) & (b) & (c) & (d) & (e) & (f) \\
\end{tabular}
\caption{Leaf alignment results on the last frame of $6$ plant videos. First row shows the original images. Second row shows the alignment results with red points denoting the boundary of the leaf templates in the blue bounding boxes. The numbers on the leaves are the leaf IDs representing the order of the leaf being selected and they will be consistent during tracking.}
\label{fig:alignResult}
\end{centering}
\end{figure*}

@@

& Day 1 & Day 2 & Day 3 & Day 4 & Day 5 & Day 6 & Day 7 & Day 8 & Day 9 \\
\end{tabular}
\caption{Tracking result for one video with one frame for each day. $(a)$ Example frames in the video. $(b)$ Leaf label results overlaid with tip locations. $(c)$ Leaf tracking results. }
\label{fig:trackExample}
\end{centering}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[width=.81\textwidth]{Figures/performance.pdf}\\
\caption{Performance of the baseline method on the testing set of the fluorescence modality of Arabidopsis plant.}
\label{fig:performance}
\end{figure*}

\subsection{Performance and Analysis}
We apply our algorithm to all $144$ frames of each video and evaluate the performance on labeled $36$ frames.
Leaf alignment is applied to the last frame of each video.
Figure~\ref{fig:alignResult} shows some examples of leaf alignment results.
Our framework works very well on segmenting large leaves with no overlap to neighbor leaves.
For overlapping leaves, it becomes more challenging as the edges in the overlapping area are more difficult to be detected.
However, when the overlapping leaves are further away from the center, they will have a higher chance to be detected as shown in $(c)$ of Figure~\ref{fig:alignResult}.
When the overlapping leaves are close to the center, smaller leaves will be covered by larger leaves as shown in $(a), (d), (e)$ of Figure~\ref{fig:alignResult}.

Leaf alignment provides the leaf candidates for tracking over time. 
Figure~\ref{fig:trackExample} shows the leaf tracking result of one video.
The leaf template transformation works well for most of the leaves.
As plant grows, younger leaves may grow faster than older leaves and occlude the older leaves.
As shown in Figure~\ref{fig:trackExample} (b), purple leaf replaces the red leaf at day $6$.
Our backward tracking algorithm tracks leaves from the last frame to the first frame.
The two leaves are still being considered as one leaf (ID $8$) in day $4$ and day $3$.
Leaf $8$ in day $1$ and $2$ is a leaf ID switch w.r.t.~the purple ground truth leaf and will not be considered as a consistently tracked leaf.
However, they are still evaluated as well aligned and segmented leaves.
%Leaves will be deleted when it becomes small and the leaf underneath it will be detected.

For quantitative evaluation, we vary $\tau$ from $0$ to $1$ and generate the first three evaluation metrics, as shown in Figure~\ref{fig:performance}.
{\it{ULR}} decreases as $\tau$ increases as more leaves are being considered as matched leaves.
As $\tau$ keeps increasing, {\it{ULR}} approaches a constant value, which is the different number in leaf counting that results from both miss detection and false alarms.
{\it{LE}} increases as $\tau$ increases as it includes leaves with larger tip-based errors for averaging.
{\it{TC}} increases as $\tau$ increases as more leaves are being considered as correctly tracked leaves.
Note that {\it{TC}} is influenced by the length of frames evaluated for each video.
As the longer frames we evaluate, the higher chance tracking will fail.
Overall, our method can detect $87\%$ and track $50\%$ of all labeled leaves with less than $20\%$ average tip-based errors.

### 2015-05-04 datapaper_hardware.tex
xm's first edits

\begin{figure}
  \includegraphics[width=\linewidth,trim=55 80 200 70,clip]{Figures/hardware}
\caption{The hardware setup for our data collection.}
\label{fig:hardware}
\end{figure}

@@

\subsubsection{Fluorescence and IR images}
Chlorophyll a fluorescence images were captured once every hour during the daylight period in a growth chamber~\cite{cruz2015depi}. 
A set of $5$ images were captured using a Hitachi KP-F145GV CCD camera (Hitachi Kokusai Electric America Inc., Woodbury, NY) outfitted with an infrared long pass filter (Schott Glass RG-9, Thorlabs, Newton, NJ), during a short period ($<400~ms$) of intense light saturating to photosynthesis ($>10,000~\mu mol~photons~m^{-2} s^{-1}$) provided by an array of white Cree LEDs (XMLAWT, 5700K color temperature, Digi-Key, Thief River Falls, MN) collimated using a $20~mm$ Carclo Lens (10003, LED Supply, Lakewood, CO).
%
Chlorophyll a fluorescence was excited using monochromatic red LEDs (Everlight $625~nm$, ELSH-F51R1-0LPNM-AR5R6, Digi-Key), collimated using a Ledil reflector optic ($C11347\_REGINA$, Mouser Electronics, Mansfield, TX) and pulsed for $50~\mu s$ during a brief window when the white LEDs were electronically shuttered.  
In addition, a series of $5$ images were also collected in the absence of the excitation light for artifact subtraction.

@@

\subsubsection{RGB color and depth images} %This section describes characterizes the data from this sensor, particularly the depth data.

@@

% For one-column wide figures use
\begin{figure}
\begin{tabular}{c}
  \includegraphics[width=\linewidth,trim=60 200 45 250,clip]{Figures/CameraConfiguration} \\
  ($a$)\\
  \includegraphics[width=0.65\linewidth,trim=175 220 162 180, clip,angle=-90,origin=c]{Figures/DepthOnBeanRGB} \vspace{-10mm} \\ 
  ($b$)\\
\end{tabular}
\caption{($a$)A plot of the three cameras showing their relative configuration and fields of view as obtained through calibration.  Units are in $mm$, apart from the size of the images which are scaled and plotted at equal resolution.  The optical center of the color camera (left-most) defines the world coordinate system.  Close to it is the depth camera having much lower resolution.  The right-most camera is the combined fluorescent and IR camera. ($b$) $3$D points from the depth camera are projected along their rays into the world coordinates and then projected into the color and fluorescent camera images.  This shows the projection into the color image (with $90^{\circ}$ rotation for economical use of space).  Only points in a rectangular region around the plant in the depth image are selected, and these are further filtered by eliminating points with high standard deviation.  An algorithm requiring only $3$D points on the plant could select only those that fall on the leaf pixels.}
\label{fig:CameraConfiguration}
\end{figure}

>>>>

\begin{figure}
  \includegraphics[width=\linewidth,trim=55 100 200 70,clip]{Figures/hardware}
\caption{The hardware setup for our data collection.}
\label{fig:hardware}
\end{figure}

@@

\subsubsection{Fluorescence and IR Images}
Chlorophyll a fluorescence images were captured once every hour during the daylight period in a growth chamber~\cite{cruz2015depi}.
A set of $5$ images were captured using a Hitachi KP-F145GV CCD camera (Hitachi Kokusai Electric America Inc., Woodbury, NY) outfitted with an infrared long pass filter (Schott Glass RG-9, Thorlabs, Newton, NJ), during a short period ($<400~ms$) of intense light saturating to photosynthesis ($>10,000~\mu mol~photons~m^{-2} s^{-1}$) provided by an array of white Cree LEDs (XMLAWT, 5700K color temperature, Digi-Key, Thief River Falls, MN) collimated using a $20~mm$ Carclo Lens (10003, LED Supply, Lakewood, CO).
%
Chlorophyll a fluorescence was excited using monochromatic red LEDs (Everlight $625~nm$, ELSH-F51R1-0LPNM-AR5R6, Digi-Key), collimated using a Ledil reflector optic ($C11347\_REGINA$, Mouser Electronics, Mansfield, TX) and pulsed for $50~\mu s$ during a brief window when the white LEDs were electronically shuttered.
In addition, a series of $5$ images were also collected in the absence of the excitation light for artifact subtraction.

@@

\subsubsection{RGB Color and Depth Images} %This section describes characterizes the data from this sensor, particularly the depth data.

@@

% For one-column wide figures use
\begin{figure}
\begin{tabular}{c}
  \includegraphics[width=\linewidth,trim=120 240 80 300,clip]{Figures/CameraConfiguration} \\
  ($a$)\\
  \includegraphics[width=0.65\linewidth,trim=175 220 162 180, clip,angle=-90,origin=c]{Figures/DepthOnBeanRGB} \vspace{-10mm} \\
  ($b$)\\
\end{tabular}
\caption{($a$)A plot of the three cameras showing their relative configuration and fields of view as obtained through calibration.  Units are in $mm$, apart from the size of the images which are scaled and plotted at equal resolution.  The optical center of the color camera (left-most) defines the world coordinate system.  Close to it is the depth camera having much lower resolution.  The right-most camera is the combined fluorescent and IR camera. ($b$) $3$D points from the depth camera are projected along their rays into the world coordinates and then projected into the color and fluorescent camera images.  This shows the projection into the color image (with $90^{\circ}$ rotation for economical use of space).  Only points in a rectangular region around the plant in the depth image are selected, and these are further filtered by eliminating points with high standard deviation.  An algorithm requiring only $3$D points on the plant could select only those that fall on the leaf pixels.}
\label{fig:CameraConfiguration}
\end{figure}

### 2015-05-04 datapapr_labeling.tex
xm's first edits

\section{Annotation, Files and Protocol}
\subsection{Data statistics}
MSU-PID includes two subsets, one for each plant type: Arabidopsis and Bean.
The statistic information of these two subsets are summarized in Table~\ref{tab:stat}.
The images were acquired every hour.
As there is no light at night hours, plants can not be imaged by the fluorescence and RGB color sensors while IR and depth cameras can still perform the capturing in the night.
In order to make sure that all four modalities present at each imaging opportunity, we release the part of images captured only in the day time, which are $16$ images per day for Arabidopsis and $14$ for bean for all four modalities.

@@

\subsection{Manual annotations}
Part of the database is manually annotated to provide ground truth tip locations, leaf segmentation results and leaf consistency overtime.
Tip locations are saved in a TXT file for each frame.
Leaf segmentation results are stored in a PNG image for each frame with one color for each leaf.
The same color is used to represent the same leaf over a sequence of frames.

@@

@@

\subsection{Name conventions and file types}
We release training and testing sets in two separate folders.
In each folder, there are two subfolders named Arabidopsis and Bean.
The files in each subfolder have the following form:

\begin{itemize}
\item plant$\_$ID$\_$day$\_$X$\_$hour$\_$YY$\_$rgb.png: the original RGB color images;
\item plant$\_$ID$\_$day$\_$X$\_$hour$\_$YY$\_$fmp.png: the original fluorescence images;
\item plant$\_$ID$\_$day$\_$X$\_$hour$\_$YY$\_$ir.png: the original IR images;
\item plant$\_$ID$\_$day$\_$X$\_$hour$\_$YY$\_$depth.png: the original depth images;
\item plant$\_$ID$\_$day$\_$X$\_$hour$\_$YY$\_$depthSigma.png: the depth standard deviation images;
\item plant$\_$ID$\_$day$\_$X$\_$hour$\_$YY$\_$label.png: the labeled images of fluorescence modality;
\item plant$\_$ID$\_$day$\_$X$\_$hour$\_$YY$\_$tips.txt: the labeled tip locations;
\end{itemize}
where ID indicates the plant ID number ($1$ to $16$ for Arabidopsis, $1$ to $5$ for bean), X is an integer indicating the date ($1-9$ for Arabidopsis, $1$ to $5$ for bean), and YY represents the image index within a day ($1-16$ for Arabidopsis, $1$ to $14$ for bean).
For each combination of day and hour, we provide four modalities in PNG files ($\_$rgb, $\_$fmp, $\_$ir, $\_$depth).
%\begin{itemize}
% \item plant$\_$XX$\_$day$\_$X$\_$hour$\_$YY$\_$ID$\_$ZZ$\_$rgb.png: the original RGB color images;
% \item plant$\_$XX$\_$day$\_$X$\_$hour$\_$YY$\_$ID$\_$ZZ$\_$fmp.png: the original fluorescence images;
% \item plant$\_$XX$\_$day$\_$X$\_$hour$\_$YY$\_$ID$\_$ZZ$\_$ir.png: the original IR images;
% \item plant$\_$XX$\_$day$\_$X$\_$hour$\_$YY$\_$ID$\_$ZZ$\_$depth.png: the original depth images;
% \item plant$\_$XX$\_$day$\_$X$\_$hour$\_$YY$\_$ID$\_$ZZ$\_$label.png: the labeled images of fluorescence modality;
% \item plant$\_$XX$\_$day$\_$X$\_$hour$\_$YY$\_$ID$\_$ZZ$\_$tips.txt: the labeled tip locations;
%\end{itemize}
%where XX indicates the plant type ("AR" or "BE"), X is an integer indicating the date (e.g., $1-9$ for Arabidopsis), YY represents the image index within a day (e.g., $1-16$ for Arabidopsis), and ZZ is the subject (or plant) ID (e.g., $1-5$ for bean).
%For each combination of day and hour, we provide four modalities in PNG files ($\_$rgb, $\_$fmp, $\_$ir, $\_$depth).
For annotated images, we have two additional files ($\_$label, $\_$tips) saving the annotation results.
Leaf segmentation results are encoded as indexed PNG files, where each leaf is assigned a unique and consistent leaf ID over time.
Leaf ID starts from $1$ and continuously increase till the total number of leaves.
And the background is encoded as $0$.
Tips locations are saved in TXT files where each line has the following format:
\begin{itemize}
\item leaf ID \quad tip1$\_$x \quad tip1$\_$y \quad tip2$\_$x \quad tip2$\_$y
\end{itemize}
where leaf ID is an integer number that is consistent with the segmentation label in the PNG file.
tip1$\_$x and tip1$\_$y represent the coordinates of the outer tip point.
tip2$\_$x and tip2$\_$y represent the coordinates of the inner tip point.

>>>>

\section{Annotation, Files and Protocol}
\subsection{Data Statistics}
MSU-PID includes two subsets, one for each plant type: Arabidopsis and Bean.
The statistic information of these two subsets are summarized in Table~\ref{tab:stat}.
The images were acquired every hour.
As there is no light at night hours, plants can not be imaged by the fluorescence and RGB color sensors while IR and depth cameras can still perform the capturing in the night.
In order to make sure that all four modalities present at each imaging opportunity, we release the part of images captured only in the day time, which are $16$ images per day for Arabidopsis and $14$ for bean for all four modalities.

@@

@@

\subsection{Manual Annotations}
Part of the database is manually annotated to provide ground truth tip locations, leaf segmentation results and leaf consistency overtime.
Tip locations are saved in a TXT file for each frame.
Leaf segmentation results are stored in a PNG image for each frame with one color for each leaf.
The same color is used to represent the same leaf over a sequence of frames.

@@

\subsection{Name Conventions and File Types}
We release training and testing sets in two separate folders.
In each folder, there are two subfolders named Arabidopsis and Bean.
The files in each subfolder have the following form:

\begin{itemize}
\item plant$\_$ID$\_$day$\_$X$\_$hour$\_$YY$\_$rgb.png: the original RGB color images;
\item plant$\_$ID$\_$day$\_$X$\_$hour$\_$YY$\_$fmp.png: the original fluorescence images;
\item plant$\_$ID$\_$day$\_$X$\_$hour$\_$YY$\_$ir.png: the original IR images;
\item plant$\_$ID$\_$day$\_$X$\_$hour$\_$YY$\_$depth.png: the original depth images;
\item plant$\_$ID$\_$day$\_$X$\_$hour$\_$YY$\_$depthSigma.png: the depth standard deviation images;
\item plant$\_$ID$\_$day$\_$X$\_$hour$\_$YY$\_$label.png: the labeled images of fluorescence modality;
\item plant$\_$ID$\_$day$\_$X$\_$hour$\_$YY$\_$tips.txt: the labeled tip locations;
\end{itemize}
where ID indicates the plant subject ID number ($1$ to $16$ for Arabidopsis, $1$ to $5$ for bean), X is an integer indicating the date ($1-9$ for Arabidopsis, $1$ to $5$ for bean), and YY represents the image index within a day ($1-16$ for Arabidopsis, $1$ to $14$ for bean).
For each combination of day and hour, we provide four modalities in PNG files ($\_$rgb, $\_$fmp, $\_$ir, $\_$depth).
%\begin{itemize}
% \item plant$\_$XX$\_$day$\_$X$\_$hour$\_$YY$\_$ID$\_$ZZ$\_$rgb.png: the original RGB color images;
% \item plant$\_$XX$\_$day$\_$X$\_$hour$\_$YY$\_$ID$\_$ZZ$\_$fmp.png: the original fluorescence images;
% \item plant$\_$XX$\_$day$\_$X$\_$hour$\_$YY$\_$ID$\_$ZZ$\_$ir.png: the original IR images;
% \item plant$\_$XX$\_$day$\_$X$\_$hour$\_$YY$\_$ID$\_$ZZ$\_$depth.png: the original depth images;
% \item plant$\_$XX$\_$day$\_$X$\_$hour$\_$YY$\_$ID$\_$ZZ$\_$label.png: the labeled images of fluorescence modality;
% \item plant$\_$XX$\_$day$\_$X$\_$hour$\_$YY$\_$ID$\_$ZZ$\_$tips.txt: the labeled tip locations;
%\end{itemize}
%where XX indicates the plant type ("AR" or "BE"), X is an integer indicating the date (e.g., $1-9$ for Arabidopsis), YY represents the image index within a day (e.g., $1-16$ for Arabidopsis), and ZZ is the subject (or plant) ID (e.g., $1-5$ for bean).
%For each combination of day and hour, we provide four modalities in PNG files ($\_$rgb, $\_$fmp, $\_$ir, $\_$depth).
For annotated images, we have two additional files ($\_$label, $\_$tips) saving the annotation results.
Leaf segmentation results are encoded as indexed PNG files, where each leaf is assigned a unique and consistent leaf ID over time.
Leaf ID starts from $1$ and continuously increase till the total number of leaves.
And the background is encoded as $0$.
Tips locations are saved in TXT files where each line has the following format:
\begin{itemize}
\item leaf ID \quad tip1$\_$x \quad tip1$\_$y \quad tip2$\_$x \quad tip2$\_$y
\end{itemize}
where leaf ID is an integer number that is consistent with the segmentation label in the PNG file.
tip1$\_$x and tip1$\_$y represent the coordinates of the outer tip point.
tip2$\_$x and tip2$\_$y represent the coordinates of the inner tip point.
